---
title: "NLP"
author: "Kristof Menyhert"
output:
  pdf_document: default
  html_document: default
---
Load some packages:
```{r, message=FALSE, warning= FALSE}
library(gutenbergr)
library(tidyr)
library(tidyverse)
library(stringr)
library(tidytext)
library(tm)
library(topicmodels)
library(ggplot2)
```

#### Download some books:
```{r, message=FALSE, warning= FALSE}
books <- gutenberg_works(title %in% c("Oliver Twist",
                                      "Candide", "Dracula",
                                      "The Adventures of Sherlock Holmes")) %>%
  gutenberg_download(meta_fields = "title")

unique(books$title)
```

#### divide into documents each representing one chapter
```{r}
reg <- regex("^chapter ", ignore_case = TRUE)

by_chapter <- books %>%
  group_by(title) %>%
  mutate(chapter = cumsum(str_detect(text, reg))) %>%
  ungroup() %>%
  filter(chapter > 0) %>%
  unite(document, title, chapter)
```

#### Split into words
```{r}
by_chapter_words <- by_chapter %>% 
  unnest_tokens(word, text)
```

#### find document word count
```{r}
word_counts <- by_chapter_words %>%
  anti_join(stop_words) %>%
  count(document, word, sort = TRUE) %>%
  ungroup()
```
#### LDA on chapters

```{r}
chapters_dtm <- cast_dtm(word_counts, document, word, n)
```

#### Create k model model (now it is 4 as we have 4 books)
```{r}
chapters_lda <- LDA(chapters_dtm, k = 4, control = list(seed = 123))
chapters_lda
```


```{r}
chapter_topics <- tidy(chapters_lda, matrix = "beta")
```

This turned the model into one-topic-per-row format. For each combination, the model computes the probability of that term being generated from that topic.

#### Find top top five terms within each topic:
```{r}
top_terms <- chapter_topics %>%
  group_by(topic) %>%
  top_n(15, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)
```

#### Plot the results:
```{r}
top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = F) +
  facet_wrap(~topic, scales = "free") + 
  coord_flip()
```

Based on these graph we can guess associate which topics goes to which books.  

* 1st goes to Dracula  
* 2nd goes to Oliver Twist  
* 3rd goes to Sherlock Holmes  
* 4th goes to Candide  